\documentclass[fontsize12,a4]{article}
\usepackage{fancyhdr}

% Header and footer configuration
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{Title of Document} % Centered header
\fancyfoot[C]{Maulana Abul Kalam Azad University of Technology \quad \thepage} % Centered footer with page number

\begin{document}
\section*{Section 1}

Software development technologies are the tools and methods that developers use to design, develop, test, and deploy software applications. These include a wide range of software technologies, such as programming languages, frameworks and libraries, databases, and cloud computing platforms.Known for its high performance and efficiency, C++ is popular in game development and systems programming.
This language lets programmers control memory and hardware directly, while also making it easy to create complex algorithms and data structures.In other words, this language is both powerful and flexible.It gives programmers the control they need to write high-performance code, while also providing features that make it easier to develop complex algorithms and data structures.
\section*{Section 2}
React is a JavaScript library for building user interfaces. It is declarative, efficient, and flexible. React components are self-contained and reusable, making code easier to maintain and update.This tool is a good choice for developing user interfaces. Additionally, React is suitable for building a variety of web applications, including single-page applications.Angular is a popular JavaScript framework for building dynamic web applications. It is open source and free to use.
It uses a convention over configuration approach, which means that you don’t need to specify how to build your data models in advance. Instead, Angular provides conventions that you can follow to model your data. However, it can be difficult to use. It’s a good choice for developers who need to build complex web applications, but it may not be the best choice for beginners.

\end{document}